---
title: "Interactive County Analysis"
author: "Layla Nayfeh"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    self-contained: true
    toc: true
    toc-location: left
---

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning=FALSE,
  message=FALSE
)

library(tidyverse)
library(tigris)
library(sf)
library(tidycensus)
library(htmltools)
library(janitor)
library(here)
library(mapview)
library(leafsync)
library(leaflet.extras2)
library(writexl)
library(jsonlite)
options(tigris_class = "sf")


```

# **Interactive Analysis**

### **This is an analysis comparing Massachusetts counties' income and age!**

#### First, I'm using the tidycensus package to pull the census data and geospatial boundaries.

```{r, results = 'hide'}

census_api_key("2a6f8c21a30d3024e038d67d7d4eba647dc79cd4", overwrite=TRUE)


```

#### Next, I'm choosing my variables...

```{r, results = 'hide'}

myvars <- c(totalpop = "B01003_001",
            medincome = "B19013_001",
            medage = "B01002_001"
)
```

#### I chose to look at Massachusetts, my home state. So, now, I'm pulling Massachusetts-specific counties.

```{r, results = 'hide'}
ma_counties_withgeo <- get_acs(geography = "county",
                       variables = c(myvars),
                       state = "MA",
                       output = "wide",
                       geometry = TRUE)

ma_counties_withgeo
```

#### I'm also grabbing all U.S. counties...

```{r, results = 'hide'}

all_counties_withgeo <- get_acs(geography = "county",
                       variables = c(myvars),
                       output = "wide",
                       geometry = TRUE)

all_counties_withgeo
```

#### ...cleaning up the column names...

```{r, results = 'hide'}
ma_counties_withgeo <- ma_counties_withgeo %>%
  select(-ends_with("M"))

ma_counties_withgeo
```

```{r, results = 'hide'}
colnames(ma_counties_withgeo) <- sub("E$", "", colnames(ma_counties_withgeo)) 

ma_counties_withgeo
```

#### Now, I'm mapping Massachusetts counties with mapview.

```{r}

mapview(ma_counties_withgeo, zcol = "medincome")

```

#### Then, we customize the colors. Purple, for fun.

```{r}

mapview(ma_counties_withgeo, zcol = "medincome", 
         col.regions = RColorBrewer::brewer.pal(14, "Purples"), 
         alpha.regions = 1)

```

#### Customizing those legends

```{r}

mapview(ma_counties_withgeo, zcol = "medincome", 
         col.regions = RColorBrewer::brewer.pal(14, "Purples"), 
         alpha.regions = 1,
         legend = FALSE, 
         label = FALSE, 
         popup = FALSE)


```

#### ...the labels, too.

```{r}

mylabel <- glue::glue("{ma_counties_withgeo$NAM} {ma_counties_withgeo$medincome}")


mapview(ma_counties_withgeo, zcol = "medincome", 
         col.regions = RColorBrewer::brewer.pal(14, "Purples"), 
         alpha.regions = 1,
         label = mylabel)

```

#### ...and the popups...

```{r}
mypopup <- glue::glue("<strong>{ma_counties_withgeo$NAM}</strong><br />
                      Total Population: {ma_counties_withgeo$totalpop}<br />
                      Median Income: {ma_counties_withgeo$medincome}") %>% 
  lapply(htmltools::HTML)

# mylabel <- glue::glue("{all_data$State} {all_data$PctChange10_20}%") %>%
#   lapply(htmltools::HTML)

```

```{r, results = 'hide'}

head(mypopup)

```

```{r}

mapview(ma_counties_withgeo, zcol = "medincome", 
         col.regions = RColorBrewer::brewer.pal(14, "Purples"), 
         alpha.regions = 1,
         popup = mypopup)

```

#### Looking at our variables side by side, with my labels and popups!

```{r}

map_income <- mapview(ma_counties_withgeo, zcol = "medincome", 
         col.regions = RColorBrewer::brewer.pal(14, "Purples"), 
         alpha.regions = 1,
         popup = mypopup,
         label = mylabel)

map_age <- mapview(ma_counties_withgeo, zcol = "medage", 
         col.regions = RColorBrewer::brewer.pal(14, "Purples"), 
         alpha.regions = 1,
         popup = mypopup,
         label = mylabel)

sync(map_income, map_age)

# With a slider!
map_income | map_age

```

## Some Analysis:

#### Middlesex county seems to be the youngest and wealthiest. This might be because this county is home to Cambridge, where some of the nations top colleges are located. Interestingly, the oldest counties in Massachusetts, like Barnstable, where Cape Cod is, is not the wealthiest. While older people retire there and wealthy families summer there, the general population is most likely working class. Dukes County, home to Martha's vineyard, seems to be a similar case. Surprisingly, Nantucket, another island off the coast of Massachusetts, has a younger population that is wealthier.

# [go back home](https://laylanayfeh.github.io/laylanayfeh/)
